Hippocampal segmentation with MAGeT

### 2013-01-30 paper.Rnw
Some work on improving the literature review in the introduction
Starting to pull apart the intro

%  Automated methods 
%
%  Heckemann2006 - 
%  Heckemann2011 -  Automatic morphometry in AD and MCI 
%    - (MAPER). multi-atlas. 30 atlases, entire ADNI screening  
%  Collins2010 - .. seg of HC and AM by augmenting ANIMAL
%    - multi-atlas 80 atlases, atlas selection (NMI)
%  Aljabar2009 - atlas selection and effect on accuracy
%    - 
%  Leung2010 - X-sectional and longitudinal HC vol in MCI, AD
%    - (MAPS), multi-atlas + STAPLE. 55 atlases. baseline+1yr of ADNI seg.
%    - atrophy rates
%  Lotjonen2010 - Fast and robust
%    - IBSR/ADNI.  
%  Mouiha2011b - Hippocampal atrophy rates in AD
%    - compare SNT vs FreeSurfer on ADNI
%
Fully-automated segmentation techniques overcome the need for human expertise.
In particular, {\it atlas-based} approaches make use of one or more expertly
segmented MRIs (the atlas library) as templates to guide the segmentation of a
query subject's MRI
\cite{Aljabar2009,Collins2010,Heckemann2011,Leung2010,Lotjonen2010,Leung2010,Wolz2010}.
The basic strategy is as follows. Each atlas is warped to fit a subject's
neuroanatomy using nonlinear registration techniques
\citep{Collins1995,Klein2009}.  Atlas labels are then transformed by this
warping to the subject's space, and a {\it label fusion} technique, such as
voxel-wise voting, is used to merge the competing label definitions from each
atlas into a final segmentation for the subject.

Multi-atlas hippocampal segmentation algorithms achieve some of the best
automated segmentation accuracies to-date, and approach the performance of a
manual rater
\citep{Heckemann2011,Collins2010,Aljabar2009,Leung2010,Lotjonen2010}, but rely
on an atlas library containing anywhere between 30 and 80 expertly labeled
images to achieve this accuracy.  As already noted, the production of an atlas
library requires significant manual effort and expertise, as does the
modification of an existing atlas library in order to better suit a target
population or investigate a specific research hypothesis.  Therefore, in this
paper we tackle the problem of producing accurate segmentations using small
numbers of manually segmented atlases.

>>>>

% atlas-based methods -> a prior feature based methods?
%
% - basic multi-atlas method, 
%  Collins2010 - .. seg of HC and AM by augmenting ANIMAL
%    - multi-atlas 80 atlases, atlas selection (NMI)
%  Aljabar2009 - atlas selection and effect on accuracy
% - extensions and practical applications
%  Leung2010 - X-sectional and longitudinal HC vol in MCI, AD
%    - (MAPS), multi-atlas + STAPLE. 55 atlases. baseline+1yr of ADNI seg.
%    - atrophy rates
%  Lotjonen2010 - Fast and robust
%    - IBSR/ADNI.  
% - Coutin's use of shape-based priors
%
% - multi-atlas with specialised/small atlas libraries
%   - Fischl - freesurfer, high-resolution atlases + probability priors
%   - Yushkevitch - invivo focal HF-MRI 
%  
%  Heckemann2011 -  Automatic morphometry in AD and MCI 
%    - (MAPER). multi-atlas. 30 atlases, entire ADNI screening  
%  Mouiha2011b - Hippocampal atrophy rates in AD
%    - compare SNT vs FreeSurfer on ADNI
%
%
Fully-automated segmentation techniques require no human expertise beyond that
of an initial configuration.  Multi-atlas automated segmentation algorithms make
use of a series of expertly segmented MRIs (the atlas library) as models to
guide the segmentation of a query subject's MRI, and achieve some of the best
automated hippocampal segmentation accuracies to-date

\citep{Aljabar2009,Collins2010,Heckemann2011,Leung2010,Lotjonen2010,Leung2010,Wolz2010}.
The basic strategy is as follows. Each atlas is warped to fit a subject's
neuroanatomy using nonlinear registration techniques
\citep{Collins1995,Klein2009}.  Atlas labels are then transformed by this
warping to the subject's space, and a {\it label fusion} technique, such as
voxel-wise voting, is used to merge the competing label definitions from each
atlas into a final segmentation for the subject.

but rely
on an atlas library containing anywhere between 30 and 80 expertly labeled
images to achieve this accuracy.  As already noted, the production of an atlas
library requires significant manual effort and expertise, as does the
modification of an existing atlas library in order to better suit a target
population or investigate a specific research hypothesis.  Therefore, in this
paper we tackle the problem of producing accurate segmentations using small
numbers of manually segmented atlases.
